Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-05-17 paper/tex/paper.tex
Updates from Overleaf
new title

\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}

% affiliations
\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\newcommand{\UoA}{Anton Pannekoek Institute for Astronomy, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}

@@

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{\mpa}
\affiliation{\UoA}
\affiliation{\cfa}

@@

\author[0000-0001-5484-4987]{L. van Son}
\affiliation{\cfa}
\affiliation{\mpa}

\author[0000-0001-7969-1569]{S. Justham}
\affiliation{School of Astronomy \& Space Science, University of the Chinese Academy of Sciences, Beijing 100012, China}
\affiliation{Anton Pannekoek Institute for Astronomy and GRAPPA, University of Amsterdam, NL-1090 GE Amsterdam, The Netherlands}

>>>>

% selma's newest catchy one
\title{Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries}

% selma suggested removing BHNS
% \title{Predictions for neutron star and black hole binaries with LISA}

% original
%\title{Predictions for detecting BHNS and other double compact objects binaries with LISA}

% affiliations
\newcommand{\cfa}{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
\newcommand{\mpa}{Max-Planck-Institut für Astrophysik, Karl-Schwarzschild-Straße 1, 85741 Garching, Germany}
\newcommand{\cca}{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY, 10010, USA}
\newcommand{\UvA}{Anton Pannekoek Institute for Astronomy \& Grappa, University of Amsterdam, Postbus 94249, 1090 GE Amsterdam, The Netherlands}

@@

\author[0000-0001-9336-2825]{S. E. de Mink}
\affiliation{\mpa}
\affiliation{\UvA}
\affiliation{\cfa}

@@

\author[0000-0001-5484-4987]{L.A.C. van Son}
\affiliation{\cfa}
\affiliation{\UvA}
\affiliation{\mpa}

\author[0000-0001-7969-1569]{S. Justham}
\affiliation{School of Astronomy \& Space Science, University of the Chinese Academy of Sciences, Beijing 100012, China}
\affiliation{\UvA}
